---
title: "Data Science Workflow"
output:
  html_document:
    df_print: paged
---



1. Define the Problem
What is the problem? Provide formal and informal definitions.
Why does the problem need to be solved? Motivation, benefits, how it will be used.
How would I solve the problem? Describe how the problem would be solved manually to flush domain knowledge.
This problem definition
Company wants to automate the loan eligibility process (real time) based on customer detail provided while filling online application form. These details are Gender, Marital Status, Education, Number of Dependents, Income, Loan Amount, Credit History and others. To automate this process, they have given a problem to identify the customers segments, those are eligible for loan amount so that they can specifically target these customers.
Variable Descriptions
Variable - Description
Loan_ID - Unique Loan ID
Gender - Male/ Female
Married - Applicant married (Y/N)
Dependents - Number of dependents
Education - Applicant Education (Graduate/ Under Graduate)
Self_Employed - Self employed (Y/N)
ApplicantIncome - Applicant income
CoapplicantIncome - Coapplicant income
LoanAmount - Loan amount in thousands
Loan_Amount_Term - Term of loan in months
Credit_History - credit history meets guidelines
Property_Area - Urban/ Semi Urban/ Rural
Loan_Status - Loan approved (Y/N)
2. Prepare Data
Data Selection. Availability, what is missing, what can be removed.
Data Preprocessing. Organize selected data by formatting, cleaning and sampling.
Data Transformation. Feature engineering using scaling, attribute decomposition and attribute aggregation.
Data visualizations such as with histograms. 

```{r}
#Read training dataset in dataframe
df <- read.csv(url("https://raw.githubusercontent.com/3Blades/notebook-templates/master/python/Datasets/lp_train.csv"))
df
```
```{r}
#Reading second dataset in data frame
af <- read.csv(url("https://raw.githubusercontent.com/3Blades/notebook-templates/master/python/Datasets/lp_test.csv"))
af
```
```{r}
#Display row 1
cf <- read.csv(url("https://raw.githubusercontent.com/3Blades/notebook-templates/master/python/Datasets/lp_test.csv"), nrows = 1)
cf

```
```{r}
#Shows all non-numeric columns
nums <- sapply(df, is.factor)
df[,nums]
```

```{r}
df <- read.csv(url("https://raw.githubusercontent.com/3Blades/notebook-templates/master/python/Datasets/lp_train.csv"), na.strings = c("","NA"))

#Gender
df['Gender']

#Married
df['Married']

#Dependents
df['Dependents']

#Self_Employed
df['Self_Employed']

#LoanAmount
df['LoanAmount']

#Loan_Amount_Term
df['Loan_Amount_Term']

#Credit_History
df['Credit_History']

#Education
df['Education']

#Property_Area
df['Property_Area']

#Loan_ID
df['Loan_ID']
```


```{r}
#Shows all non-numeric columns again
nums <- sapply(df, is.factor)
df[,nums]
```

```{r}
library(randomForest)
Y <- df['Loan_Status']
Y
validation_size <- 50
set.seed(7)
train <- sample(2,nrow(df), replace = TRUE)
validation <- sample(1,nrow(df), replace = TRUE)
Y_train <- df[train == 0]
rf = randomForest(Y,data = Y_train,ntree = 50)
rf
```
```{r}
library(caret)
library(randomForest)
X <- df['Loan_Status'][,0]
Y <- df['Loan_Status'][,1]
X
Y
validation_size <- 0.20
set.seed(7)
X_train <- sample(X, size = validation_size)
X_validation <- sample(X, size = validation_size)
Y_train <- sample(X, size = validation_size)
Y_validation <- sample(X, size = validation_size)

X_train

rf = randomForest(Y_train)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

